Comparison of FDR methods on 16S microbiome data with SummarizedBenchmark

### 2017-12-14 datasets/microbiome/microbiome-SummarizedBenchmark.Rmd
Explore weird microbiome results + add CRC Baxter

---
title: "Comparison of FDR methods on GWAS with SummarizedBenchmark"
author: "Keegan Korthauer"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

@@

```{r, schubert-ubi, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="ubiquity", maxy=20)
rank_scatter(res, pvalue="pval", covariate="ubiquity")
```

@@

```{r, schubert-abun, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=20)
rank_scatter(res, pvalue="pval", covariate="ubiquity")
```

@@

```{r, schubert-benchdesign}
bd <- initializeBenchDesign()
```

Now, we're ready to construct the `SummarizedBenchmark` object, which will run
the functions specified in each method (these are actually sourced in from the
helper scripts).

```{r, GWAS1-sb, results="hide", message=FALSE, eval=FALSE}
resfile <- paste0(resdir, "schubert_summarizedBenchmark_",
                  nrow(res), ".RData")
duration <- NA
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=res, ftCols = "ind_covariate")
                          #parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sb)$data_download_link <- "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
  save(sb, file=resfile)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  load(resfile)
}
```

@@

```{r, schubert-plot, results="hide", width=15, height=15, eval=FALSE}
# plot nrejects by method overall and stratified by covariate
rejections_scatter(sb)

rejection_scatter_bins(sb, covariate="ind_covariate", bins=4)

@@

```{r, goodrich-abun, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=5, binwidth=0.05, numQ=4)
rank_scatter(res, pvalue="pval", covariate="ubiquity")
```

@@

>>>>

---
title: "Comparison of FDR methods on 16S microbiome data with SummarizedBenchmark"
author: "Claire Duvallet"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

@@

```{r, schubert-ubi, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="ubiquity", maxy=20, binwidth=0.05)
rank_scatter(res, pvalue="pval", covariate="ubiquity")
```

@@

```{r, schubert-abun, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=8, binwidth=0.05)
rank_scatter(res, pvalue="pval", covariate="mean_abun_present")
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We'll do this for a few
values of nmids, to explore its effects on the outputs.

Then, we'll construct the `SummarizedBenchmark` object, which will run
the functions specified in each method (these are actually sourced in from the
helper scripts).

```{r, schubert-sb, results="hide", message=FALSE, eval=FALSE}
for (nmids in c(5, 50, 150)){
  print(nmids)
  bd <- initializeBenchDesign(nmids=nmids)

  resfile <- paste0(resdir, "schubert_summarizedBenchmark_",
                    nrow(res), "_nmids_", nmids, ".RData")
  duration <- NA
  if (!file.exists(resfile)){
    t1 <- proc.time()
    sb <- bd %>% buildBench(data=res, ftCols = "ind_covariate")
                            #parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sb)$data_download_link <- "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
    save(sb, file=resfile)
    duration <- round((proc.time()-t1)[3]/60,1)
  }else{
    load(resfile)
  }
}

Just for future runs, where I load the file instead of re-calculating it, here are the errors I got:

```
[1] 5
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !NaNs produced<simpleError in if (sum(D^2) > qchisq(0.9, nmids - 2 - df)) {    warning(paste0("f(z) misfit = ", round(D, 1), ".  Rerun with increased df."))}: missing value where TRUE/FALSE needed>

[1] 50
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !f(z) misfit = -21.6.  Rerun with increased df.f(z) misfit = -22.5.  Rerun with increased df.f(z) misfit = -10.  Rerun with increased df.f(z) misfit = 32.  Rerun with increased df.f(z) misfit = 14.  Rerun with increased df.f(z) misfit = -32.2.  Rerun with increased df.f(z) misfit = 6.9.  Rerun with increased df.f(z) misfit = -1.3.  Rerun with increased df.f(z) misfit = 0.7.  Rerun with increased df.f(z) misfit = 3.4.  Rerun with increased df.f(z) misfit = 5.5.  Rerun with increased df.f(z) misfit = 0.1.  Rerun with increased df.f(z) misfit = -0.9.  Rerun with increased df.f(z) misfit = -1.5.  Rerun with increased df.f(z) misfit = -1.9.  Rerun with increased df.f(z) misfit = -0.8.  Rerun with increased df.f(z) misfit = -2.4.  Rerun with increased df.f(z) misfit = 1.7.  Rerun with increased df.f(z) misfit = 0.5.  Rerun with increased df.f(z) misfit = 2.  Rerun with increased df.f(z) misfit = 0.1.  Rerun with increased df.f(z) misfit = 1.4.  Rerun with increased df.f(z) misfit = 0.2.  Reru... <truncated>

[1] 150
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !f(z) misfit = 83.4.  Rerun with increased df.f(z) misfit = -8.5.  Rerun with increased df.f(z) misfit = -13.6.  Rerun with increased df.f(z) misfit = -17.1.  Rerun with increased df.f(z) misfit = -6.4.  Rerun with increased df.f(z) misfit = -19.5.  Rerun with increased df.f(z) misfit = -17.8.  Rerun with increased df.f(z) misfit = -3.  Rerun with increased df.f(z) misfit = -21.1.  Rerun with increased df.f(z) misfit = 28.6.  Rerun with increased df.f(z) misfit = -26.  Rerun with increased df.f(z) misfit = 59.3.  Rerun with increased df.f(z) misfit = -17.1.  Rerun with increased df.f(z) misfit = 12.1.  Rerun with increased df.f(z) misfit = -28.3.  Rerun with increased df.f(z) misfit = -27.6.  Rerun with increased df.f(z) misfit = 83.7.  Rerun with increased df.f(z) misfit = -10.5.  Rerun with increased df.f(z) misfit = -22.6.  Rerun with increased df.f(z) misfit = -23.3.  Rerun with increased df.f(z) misfit = 37.3.  Rerun with increased df.f(z) misfit = -18.  Rerun with increased df.f(z... <truncated>>
```

@@

Debugging note: to look at the matrix of qvalues, run `assays(sb)[["qvalue"]]`

```{r, schubert-plot, results="hide", width=15, height=15, eval=FALSE}
# don't plot scott theoretical for now
rmv.scott <- which(grepl("scott", colnames(sb)))

# plot nrejects by method overall and stratified by covariate
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)

rejection_scatter_bins(sb, covariate="ind_covariate", bins=4, supplementary=FALSE)

# upset plot (only plot IHW for the plotted alpha)
rmv.ihw <- which(grepl("ihw", colnames(sb)) &
                              colData(sb)$param.alpha != 0.05)
rmv.cols <- c(rmv.ihw, rmv.scott)

plotMethodsOverlap(sb[,-rmv.cols], 
                   alpha=0.05, nsets=ncol(sb)-length(rmv.cols),
                   order.by="freq", decreasing=TRUE)

# upset plot excluding "unadjusted"
plotMethodsOverlap(sb[,-c(1,rmv.cols)], 
                   alpha=0.05, nsets=ncol(sb)-length(rmv.cols)-1,
                   order.by="freq", decreasing=TRUE)
```

Hm, now the code runs. However, there are clearly still some issues:
- ashs rejects all hypotheses (all q-values are essentially 0).
- lfdr and scott-empirical are all NaN (I think this is likely related to the df error)

```{r, eval=FALSE}
assays(sb)[["qvalue"]][ , 15] %>% max()
sum(is.na(assays(sb)[["qvalue"]][ , 22]))
sum(is.na(assays(sb)[["qvalue"]][ , 20]))
```

Rather than de-bug this dataset (which might be weird), let's try instead to work with the obesity dataset and see if I get the same problems.

@@

```{r, goodrich-abun, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=5, binwidth=0.05, numQ=4)
rank_scatter(res, pvalue="pval", covariate="mean_abun_present")
```

@@

Next, we'll construct the `SummarizedBenchmark` object, which will run
the functions specified in each method (these are actually sourced in from the
helper scripts).

```{r, goodrich-sb, results="hide", message=FALSE, eval=FALSE}
for (nmids in c(5, 50, 150)){
  print(nmids)
  bd <- initializeBenchDesign(nmids=nmids)

  resfile <- paste0(resdir, "goodrich_summarizedBenchmark_",
                    nrow(res), "_nmids_", nmids, ".RData")
  duration <- NA
  if (!file.exists(resfile)){
    t1 <- proc.time()
    sb <- bd %>% buildBench(data=res, ftCols = "ind_covariate")
                            #parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sb)$data_download_link <- "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
    save(sb, file=resfile)
    duration <- round((proc.time()-t1)[3]/60,1)
  }else{
    load(resfile)
  }
}
```

The outputs of this call are:

```
[1] 5
Squarem-1
Objective fn: 715262
Objective fn: 104929  Extrapolation: 0  Steplength: 1
Objective fn: 95918.9  Extrapolation: 1  Steplength: 2.44204
Objective fn: 95614.3  Extrapolation: 1  Steplength: 2.72536
Objective fn: 95583.3  Extrapolation: 1  Steplength: 2.8568
Objective fn: 95578.1  Extrapolation: 1  Steplength: 3.54373
Objective fn: 95576.3  Extrapolation: 1  Steplength: 3.52004
Objective fn: 95575.4  Extrapolation: 1  Steplength: 4
.
.
.
NaNs produced<simpleError in if (sum(D^2) > qchisq(0.9, nmids - 2 - df)) {    warning(paste0("f(z) misfit = ", round(D, 1), ".  Rerun with increased df."))}: missing value where TRUE/FALSE needed>

[1] 50
Squarem-1
Objective fn: 715262
Objective fn: 104929  Extrapolation: 0  Steplength: 1
Objective fn: 95918.9  Extrapolation: 1  Steplength: 2.44204
Objective fn: 95614.3  Extrapolation: 1  Steplength: 2.72536
Objective fn: 95583.3  Extrapolation: 1  Steplength: 2.8568
Objective fn: 95578.1  Extrapolation: 1  Steplength: 3.54373
Objective fn: 95576.3  Extrapolation: 1  Steplength: 3.52004
Objective fn: 95575.4  Extrapolation: 1  Steplength: 4
Objective fn: 95574.9  Extrapolation: 1  Steplength: 3.36769
Objective fn: 95574.5  Extrapolation: 1  Steplength: 5.09115
Objective fn: 95574.3  Extrapolation: 1  Steplength: 2.52066
Objective fn: 95574  Extrapolation: 1  Steplength: 13.3966
.
.
.
Objective fn: 95572.9  Extrapolation: 1  Steplength: 1.61619
f(z) misfit = -8.7.  Rerun with increased df.f(z) misfit = 33.3.  Rerun with increased df.f(z) misfit = -9.4.  Rerun with increased df.f(z) misfit = -37.3.  Rerun with increased df.f(z) misfit = 49.2.  Rerun with increased df.f(z) misfit = -36.9.  Rerun with increased df.f(z) misfit = 10.6.  Rerun with increased df.f(z) misfit = 13.3.  Rerun with increased df.f(z) misfit = -18.3.  Rerun with increased df.f(z) misfit = 20.1.  Rerun with increased df.f(z) misfit = -21.6.  Rerun with increased df.f(z) misfit = 23.4.  Rerun with increased df.f(z) misfit = -27.  Rerun with increased df.f(z) misfit = 17.2.  Rerun with increased df.f(z) misfit = -8.2.  Rerun with increased df.f(z) misfit = 4.3.  Rerun with increased df.f(z) misfit = 3.4.  Rerun with increased df.f(z) misfit = 2.4.  Rerun with increased df.f(z) misfit = -2.3.  Rerun with increased df.f(z) misfit = -10.7.  Rerun with increased df.f(z) misfit = -2.4.  Rerun with increased df.f(z) misfit = 15.4.  Rerun with increased df.f(z) misf... <truncated>

[1] 150
Squarem-1
Objective fn: 715262
Objective fn: 104929  Extrapolation: 0  Steplength: 1
Objective fn: 95918.9  Extrapolation: 1  Steplength: 2.44204
Objective fn: 95614.3  Extrapolation: 1  Steplength: 2.72536
Objective fn: 95583.3  Extrapolation: 1  Steplength: 2.8568
Objective fn: 95578.1  Extrapolation: 1  Steplength: 3.54373
Objective fn: 95576.3  Extrapolation: 1  Steplength: 3.52004
Objective fn: 95575.4  Extrapolation: 1  Steplength: 4
Objective fn: 95574.9  Extrapolation: 1  Steplength: 3.36769
Objective fn: 95574.5  Extrapolation: 1  Steplength: 5.09115
Objective fn: 95574.3  Extrapolation: 1  Steplength: 2.52066
Objective fn: 95574  Extrapolation: 1  Steplength: 13.3966
.
.
.
f(z) misfit = -20.2.  Rerun with increased df.f(z) misfit = 13.6.  Rerun with increased df.f(z) misfit = -3.8.  Rerun with increased df.f(z) misfit = 9.  Rerun with increased df.f(z) misfit = -21.2.  Rerun with increased df.f(z) misfit = 28.8.  Rerun with increased df.f(z) misfit = 41.9.  Rerun with increased df.f(z) misfit = -13.2.  Rerun with increased df.f(z) misfit = -12.8.  Rerun with increased df.f(z) misfit = 15.2.  Rerun with increased df.f(z) misfit = -18.1.  Rerun with increased df.f(z) misfit = -19.1.  Rerun with increased df.f(z) misfit = -18.6.  Rerun with increased df.f(z) misfit = -26.  Rerun with increased df.f(z) misfit = -7.2.  Rerun with increased df.f(z) misfit = 67.1.  Rerun with increased df.f(z) misfit = 27.2.  Rerun with increased df.f(z) misfit = -16.4.  Rerun with increased df.f(z) misfit = -21.1.  Rerun with increased df.f(z) misfit = -25.9.  Rerun with increased df.f(z) misfit = -7.5.  Rerun with increased df.f(z) misfit = 10.1.  Rerun with increased df.f(z)... <truncated>
```

```{r, goodrich-metrics, eval=FALSE}
# rename assay to qvalue
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

Debugging note: to look at the matrix of qvalues, run `assays(sb)[["qvalue"]]`

```{r, goodrich-plot, results="hide", width=15, height=15, eval=FALSE}

# plot nrejects by method overall and stratified by covariate
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)

rejection_scatter_bins(sb, covariate="ind_covariate", bins=4, supplementary=FALSE)

Hm, looks like all of the methods run without giving NaN's with nmids = 150 or lower...
But the results still aren't right.

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashs"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))

### CRC Baxter - colorectal cancer

Next, I'll look at the CRC Baxter dataset. For colorectal cancer, we do expect some amount of truly differentially abundant OTUs, but not as many as in diarrhea. This dataset will hopefully provide an intermediate non-extreme case study.
We'll download the processed OTU tables from Zenodo and unzip them in the 
`benchmark-fdr/datasets/microbiome/DATA` folder.

```{bash, baxter-download, eval=FALSE}
cd /Users/claire/github/benchmark-fdr/datasets/microbiome/DATA/
curl -O "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
tar -xzvf crc_baxter_results.tar.gz
cd ..
```

```{r, baxter-readdata}
otu_path = paste0(datdir, "crc_baxter_results/RDP/crc_baxter.otu_table.100.denovo.rdp_assigned")
meta_path = paste0(datdir, "crc_baxter_results/crc_baxter.metadata.txt")

# DiseaseState labels to keep
labels <- c("H", "CRC")

# Metadata column that has sample IDs
col_label <- "Sample_Name_s"

# Add "X" in front of sample IDs because of how R read in the OTU table
meta[, 1] <- sub("^", "X", meta[, 1])

After we've removed any shallow samples, we'll convert the OTU table to relative
abundances. I'll add a pseudo-count of 1e-7 to any zero entries, to avoid
problems with taking logs.

```{r, baxter-cleandata}
remove_shallow_smpls <- function(df, n_reads) {
  # Removes samples with fewer than n_reads from dataframe df.
  # df has OTUs in rows and samples in columns
  return(df[, colSums(df) > n_reads])
  }

# Add pseudo counts
#minabun <- min(abun_otu[abun_otu > 0]) # Use this to figure out what pseudo-count value to add
zeroabun <- 1e-7
abun_otu <- abun_otu + zeroabun

Next, we need to calculate the pvalues, effect size, and standard error for each OTU.
Here, we'll compare CRC vs. healthy. We won't consider the nonCRC adenoma patients.
We'll put these results into a dataframe, and label the columns with the 
standardized names for downstream use (`pval`, `SE`, `effect_size`, `test_statistic`).
The test statistic is the one returned by `wilcox.test()`.

```{r, baxter-pvals}
resfile <- paste0(resdir, "baxter_results_",
                  nrow(abun_otu), "_OTUs.RData")
if (!file.exists(resfile)){
  # Get case and control indices
  case_idx <- meta$DiseaseState %in% c("CRC")
  ctrl_idx <- meta$DiseaseState %in% c("H")

```{r, baxter-addphylo}
res <- res %>% separate(otu, 
                        c("kingdom", "phylum", "class", "order", "family", "genus", "species", "denovo"), 
                        sep=";", remove = FALSE)

```{r, baxter-ubi, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="ubiquity", maxy=10, binwidth=0.05)
rank_scatter(res, pvalue="pval", covariate="ubiquity")
```

Something weird is happening with p=0.20 and p=0.40 - maybe this has something to do with ties?
Either way, ubiquity looks to be a bit informative (from the scatter plot, but not really the histograms...)

```{r, baxter-abun, fig.width=10, fig.height=3.5}
strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=8, binwidth=0.05)
rank_scatter(res, pvalue="pval", covariate="mean_abun_present")
```

```{r, baxter-phylo, fig.width=10, fig.height=6}
#strat_hist(res, pvalue="pval", covariate="mean_abun_present", maxy=20)
#rank_scatter(res, pvalue="pval", covariate="ubiquity")
ggplot(res, aes(x=pval)) + geom_histogram() + facet_wrap(~phylum, scales = "free")
```

Not really informative either...

```{r, baxter-labelcovariate}
res <- res %>% mutate(ind_covariate = ubiquity)
```

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object. We'll do this for a few
values of nmids, to explore its effects on the outputs.

Then, we'll construct the `SummarizedBenchmark` object, which will run
the functions specified in each method (these are actually sourced in from the
helper scripts).

```{r, baxter-sb, results="hide", message=FALSE, eval=FALSE}
for (nmids in c(5, 50, 150)){
  print(nmids)
  bd <- initializeBenchDesign(nmids=nmids)

  resfile <- paste0(resdir, "baxter_summarizedBenchmark_",
                    nrow(res), "_nmids_", nmids, ".RData")
  duration <- NA
  if (!file.exists(resfile)){
    t1 <- proc.time()
    sb <- bd %>% buildBench(data=res, ftCols = "ind_covariate")
                            #parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sb)$data_download_link <- "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    save(sb, file=resfile)
    duration <- round((proc.time()-t1)[3]/60,1)
  }else{
    load(resfile)
  }
}

Just for future runs, where I load the file instead of re-calculating it, here are the errors I got:

```
[1] 5
Squarem-1
Objective fn: 944053
Objective fn: 111059  Extrapolation: 0  Steplength: 1
Objective fn: 92567.2  Extrapolation: 1  Steplength: 2.85015
Objective fn: 91136.8  Extrapolation: 1  Steplength: 2.70993
Objective fn: 90930.1  Extrapolation: 1  Steplength: 4
.
.
.
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !NaNs produced<simpleError in if (sum(D^2) > qchisq(0.9, nmids - 2 - df)) {    warning(paste0("f(z) misfit = ", round(D, 1), ".  Rerun with increased df."))}: missing value where TRUE/FALSE needed>

[1] 50
Squarem-1
Objective fn: 944053
Objective fn: 111059  Extrapolation: 0  Steplength: 1
Objective fn: 92567.2  Extrapolation: 1  Steplength: 2.85015
Objective fn: 91136.8  Extrapolation: 1  Steplength: 2.70993
Objective fn: 90930.1  Extrapolation: 1  Steplength: 4
.
.
.
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !f(z) misfit = -33.4.  Rerun with increased df.f(z) misfit = -40.5.  Rerun with increased df.f(z) misfit = 207.5.  Rerun with increased df.f(z) misfit = -33.  Rerun with increased df.f(z) misfit = -13.  Rerun with increased df.f(z) misfit = -35.  Rerun with increased df.f(z) misfit = -44.7.  Rerun with increased df.f(z) misfit = -38.4.  Rerun with increased df.f(z) misfit = -35.2.  Rerun with increased df.f(z) misfit = -59.5.  Rerun with increased df.f(z) misfit = 275.  Rerun with increased df.f(z) misfit = -30.1.  Rerun with increased df.f(z) misfit = -74.7.  Rerun with increased df.f(z) misfit = -87.9.  Rerun with increased df.f(z) misfit = -85.1.  Rerun with increased df.f(z) misfit = 268.2.  Rerun with increased df.f(z) misfit = -56.9.  Rerun with increased df.f(z) misfit = -39.4.  Rerun with increased df.f(z) misfit = -8.8.  Rerun with increased df.f(z) misfit = -35.6.  Rerun with increased df.f(z) misfit = -30.2.  Rerun with increased df.f(z) misfit = -14.3.  Rerun with increased ... <truncated>

[1] 150
Squarem-1
Objective fn: 944053
Objective fn: 111059  Extrapolation: 0  Steplength: 1
Objective fn: 92567.2  Extrapolation: 1  Steplength: 2.85015
Objective fn: 91136.8  Extrapolation: 1  Steplength: 2.70993
Objective fn: 90930.1  Extrapolation: 1  Steplength: 4
Objective fn: 90882.9  Extrapolation: 0  Steplength: 1
.
.
.
Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !Censored sample for null model estimation has only size 0 !f(z) misfit = -15.9.  Rerun with increased df.f(z) misfit = 8.3.  Rerun with increased df.f(z) misfit = -10.8.  Rerun with increased df.f(z) misfit = -18.1.  Rerun with increased df.f(z) misfit = -24.6.  Rerun with increased df.f(z) misfit = -27.1.  Rerun with increased df.f(z) misfit = -24.6.  Rerun with increased df.f(z) misfit = -18.8.  Rerun with increased df.f(z) misfit = -21.4.  Rerun with increased df.f(z) misfit = 279.5.  Rerun with increased df.f(z) misfit = 83.1.  Rerun with increased df.f(z) misfit = -27.4.  Rerun with increased df.f(z) misfit = -28.3.  Rerun with increased df.f(z) misfit = -7.4.  Rerun with increased df.f(z) misfit = 11.6.  Rerun with increased df.f(z) misfit = -18.2.  Rerun with increased df.f(z) misfit = -23.  Rerun with increased df.f(z) misfit = -16.7.  Rerun with increased df.f(z) misfit = -24.1.  Rerun with increased df.f(z) misfit = -23.2.  Rerun with increased df.f(z) misfit = -24.4.  Rerun with increased df.f(z) misfit = -26.6.  Rerun with increase... <truncated>> 
```

```{r, baxter-metrics, eval=FALSE}
# rename assay to qvalue
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

Debugging note: to look at the matrix of qvalues, run `assays(sb)[["qvalue"]]`

```{r, baxter-plot, results="hide", width=15, height=15, eval=FALSE}
# don't plot scott theoretical for now
rmv.scott <- which(grepl("scott", colnames(sb)))

# plot nrejects by method overall and stratified by covariate
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)

rejection_scatter_bins(sb, covariate="ind_covariate", bins=4, supplementary=FALSE)

# upset plot (only plot IHW for the plotted alpha)
rmv.ihw <- which(grepl("ihw", colnames(sb)) &
                              colData(sb)$param.alpha != 0.05)
rmv.cols <- c(rmv.ihw, rmv.scott)

plotMethodsOverlap(sb[,-rmv.cols], 
                   alpha=0.05, nsets=ncol(sb)-length(rmv.cols),
                   order.by="freq", decreasing=TRUE)

# upset plot excluding "unadjusted"
plotMethodsOverlap(sb[,-c(1,rmv.cols)], 
                   alpha=0.05, nsets=ncol(sb)-length(rmv.cols)-1,
                   order.by="freq", decreasing=TRUE)
```

```{r, eval=FALSE}
assays(sb)[["qvalue"]][, "ashs"] %>% max()
sum(is.na(assays(sb)[["qvalue"]][, "scott-empirical"]))
sum(is.na(assays(sb)[["qvalue"]][, "lfdr"]))
